---
title: "Homework 4"
author: "Luke Todd"
date: "2023-05-26"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Packages
```{r}
library(here)
library(tidyverse)
library(car)
library(sqldf)
library(janitor)
library(ggthemes)
library(naniar)
library(performance)
library(flextable)
library(broom)
library(ggeffects)
```

# Loading data
```{r}
raw_data <- read_csv(here('ntl6_v12.csv'))
```

# Problem 1
Mathematical:  
H0: $\beta_1$ = 0  
H1: $\beta_1$ != 0  

Biological:  
H0: Fish length is not a significant predictor of fish weight for trout perch.  
H1: Fish length is a significant predictor of fish weight for trout perch.  

# Problem 2
```{r}
# cleaning data
fish_data <- sqldf("SELECT year4, spname, length, weight FROM raw_data
                    WHERE spname = 'TROUTPERCH'")

# missing data viz
vis_miss(fish_data)
```

Figure 1: This figure shows that there are no missing values for year4, spname, and length, but 41% of the data is missing for weight.

# Problem 3
```{r}
fish_lm <- lm(weight ~ length, data = fish_data) # linear model
fish_res <- fish_lm$residuals # calc residuals
```

# Problem 4
```{r, fig.height=6, fig.width=7}
par(mfrow = c(2,2)) # plots two next to each other
plot(fish_lm) # plotting
```
Figure 2: This figure contains four different diagnostic plots.

# Problem 5




