---
title: "Homework 4"
author: "Luke Todd"
date: "2023-05-26"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Packages
```{r}
library(here)
library(tidyverse)
library(car)
library(sqldf)
library(janitor)
library(ggthemes)
library(naniar)
library(performance)
library(flextable)
library(broom)
library(ggeffects)
```

# Loading data
```{r}
raw_data <- read_csv(here('ntl6_v12.csv'))
```

# Problem 1
Mathematical:  
H0: $\beta_1$ = 0  
H1: $\beta_1$ != 0  

Biological:  
H0: Fish length is not a significant predictor of fish weight for trout perch.  
H1: Fish length is a significant predictor of fish weight for trout perch.  

# Problem 2
```{r}
# cleaning data
fish_data <- sqldf("SELECT year4, spname, length, weight FROM raw_data
                    WHERE spname = 'TROUTPERCH'")

# missing data viz
vis_miss(fish_data)
```

Figure 1: This figure shows that there are no missing values for year4, spname, and length, but 41% of the data is missing for weight.

# Problem 3
```{r}
fish_lm <- lm(weight ~ length, data = fish_data) # linear model
fish_res <- fish_lm$residuals # calc residuals
```

# Problem 4
```{r, fig.height=6, fig.width=7}
par(mfrow = c(2,2)) # plots two next to each other
plot(fish_lm) # plotting
```
Figure 2: This figure contains four different diagnostic plots.

# Problem 5
The residuals vs. fitted plot shows linearity and constant variance. Based on the plot, the points seem to be randomly distributed.  

The QQ norm plot is used to test if a dataset is normally distributed. Based on the plot, it appears to be normally distributed.  

The scale location plot is used to show homoscedasticity of variance. Based on the plot, the data seems to be randomly distributed.  

The residuals vs. leverage shows influential data points. Based on the plot, there appear to be some high leverage points.  

# Problem 6
```{r}
summary(fish_lm)
```

# Problem 7
```{r}
fish_anova <- anova(fish_lm) # anova table

# pulled from workshop 7
fish_table <- tidy(fish_anova) %>% 
                      #round the sum of squares and mean squares columns to have 5 digits
                      mutate(across(sumsq:meansq, ~ round(.x, digits = 5))) %>%  
                      #round the F-statistic to have 1 digit
                      mutate(statistic = round(statistic, digits = 1)) %>%  
                      #replace the very very very small p value with < 0.001
                      mutate(p.value = case_when(
                             p.value < 0.001 ~ "< 0.001")) %>%  
                      #rename the stem_length cell to be meaningful
                      mutate(term = case_when( term == "length" ~ "Fish Length (mm)",
                             TRUE ~ term)) %>% 
                      #make the data frame a flextable object
                      flextable() %>% 
                      #change the header labels to be meaningful
                      set_header_labels(df = "Degrees of Freedom", 
                                        sumsq = "Sum of squares",
                                        meansq = "Mean squares",
                                        statistic = "F-statistic",
                                        p.value = "p-value") 
fish_table
```

# Problem 8
This table shares a lot of the same information as the summary() including the f-statistic, p-value, and degrees of freedom. 

# Problem 9
With the data passing all diagnostic checks in problem 4, I was able to run a linear regression model to investigate the relationship between length and weight in trout. This linear regression, as shown in the table in problem 7, calculated a p-value of < 0.001, showing that length is a significant predictor of weight in trout. 

# Problem 10
```{r}
# extract model predictions
predictions <- ggpredict(fish_lm, terms = "length")
predictions

# visualization code
plot_predictions <- ggplot(data = fish_data, aes(x = length, y = weight)) + 
    geom_point() + # add points
    geom_line(data = predictions, 
              aes(x = x, y = predicted), 
              color = 'lightblue', 
              linewidth = 1) + # add regression line
    geom_ribbon(data = predictions, aes(x = x, # add confid. interval
                                        y = predicted, 
                                        ymin = conf.low, 
                                        ymax = conf.high), 
                alpha = 0.2) +
    theme_classic() + # add theme
    labs(x = 'Fish Length (mm)', y = 'Fish Weight (g)', # add labels and caption
         title = 'Fish Length as a Predictor of Fish Weight', 
         caption = "Figure 3: Fish lengths and weights against predicted values, shown with confidence interval.") +
    theme(plot.caption = element_text(hjust = 0), # adjustments
          text = element_text(family = 'Helvetica')) 

plot_predictions
```

Link to repo:  
https://github.com/lukegtodd/ENVS-193DS_homework-04_todd-luke 

